\fancyhf{}
\fancyfoot[C]{\zihao{-5}\tnr\thepage}
\renewcommand{\headrulewidth}{0pt}
\pagenumbering{Roman}
\begin{abstract}
    \zihao{-4}
    \setlength{\baselineskip}{20pt}
    
    在新冠疫情对经济社会的冲击影响下，许多传统的线下实体行业开始将业务转至线上、拥抱数字信息科技。并且由于新冠疫情对人类健康卫生的危害，人们出行佩戴口罩早已司空见惯，这也给传统的人脸识别系统带来了很大的挑战。

    本文针对中小型工厂企业需要快速适应新冠疫情产生的数字化转型影响，使用Django框架开发一套智慧工厂管理系统，使得工厂企业的管理人员可以快速调整工厂的业务需求，并且解决工厂企业管理人员对工厂日常信息的半手工管理方式的繁琐性与不协调性等问题。

    本文使用MaskTheFace工具对CASIA-Webface人脸数据集进行模拟佩戴口罩来构造训练数据集，对基于TripletLoss损失函数的Facenet预训练网络模型进行微调，用于解决佩戴口罩后的人脸识别准确率下降的问题。最终本文在MFR2现实世界环境下的真实佩戴口罩人脸测试数据集之上实现了95.27\%的准确率。

    \vspace{\baselineskip}\bfseries\heiti 关键词：
    \normalfont\heiti 智慧工厂；口罩人脸识别；口罩人脸数据集
\end{abstract}

\newpage
\ctexset{abstractname=\zihao{3}\tnr\bfseries\centering Abstract\vspace{.75\baselineskip}}
\begin{abstract}
    \zihao{-4}
    \tnr
    \setlength{\baselineskip}{20pt}

    Under the impact of the COVID-19 epidemic on the economy and society, many traditional offline brick-and-mortar industries have started to shift their business to online and embrace digital information technology. And due to the health hazards of the COVID-19 epidemic, it has become commonplace for people to wear masks when traveling, which also poses a great challenge to traditional face recognition systems.

    In this paper, we use the Django framework to develop a smart factory management system for small and medium-sized factories that need to quickly adapt to the digital transformation impact of the COVID-19 epidemic, so that factory managers can quickly adjust the business needs of the factory and solve the problems of tedious and uncoordinated semi-manual management of factory information by factory managers.

    In this paper, we use MaskTheFace tool to simulate the wearing of mask on CASIA-Webface face dataset to construct the training dataset and fine-tune the Facenet pretrained neural network model based on TripletLoss loss function to solve the problem of face recognition accuracy degradation after wearing the mask. Finally, this paper achieves an accuracy 95.27\% on the real mask-wearing face test dataset in the real-world environment dataset MFR2.

    \vspace{\baselineskip}\zihao{-4}\tnr\bfseries Keywords:
    \zihao{-4}\tnr\normalfont smart factory; maked face recognition; masked face dataset
\end{abstract}
